title

### 2023-11-01 outputs/paper/paper.qmd
paper edits

```{}
```

@@

![Comparing the Performance for Downsampled and Original Data](images/downsamplevsorig)

@@

@@

    -   Not danceable.

    -   Not danceable, but it does seem like it's trying to get your body to do something.

    -   More anthemic than danceable. It also seems like it's trying to coercing your attention, if not your body, and the speechiness, loudness, and energy are all apparent. The valence is apparent in the lyrics, but it doesn't have the kind of rhythm for dancing.

    -

@@

#### Could our model just be predicting Jack via Taylor Swift?

So another issue is that there is a lot of Taylor Swift in our training data. As mentioned earlier, her songs take up 40% of @tbl-mostdanceable, which is 5% more than Antonoff's own band, Bleachers. Taylor Swift has the second highest average danceability score across all songs, and the most danceable songs are hers. She also happens to have a lot of collaborations with Antonoff under her belt -- more than any other artist. I suspect that perhaps our model was predicting Jack via Taylor, which could be a beautiful story about collaboration and aesthetic affinity. Or it could suggest that this model has a stink to it. An avenue for future study.

df |>
  filter(jack == 1) |>
  ggplot(aes(x = artist_name, y = danceability)) +
  geom_boxplot() +
  ggtitle("Boxplot of Danceability by Artist") +
  coord_flip() +
  theme_minimal()
```

df |>
  filter(jack == 1) |>
  count(artist_name) |>
  arrange(desc(n)) |>
  head(10) |>
  ggplot(aes(x = reorder(artist_name, n), y = n)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  coord_flip() +
  labs(title = "Artists with Most Jack = 1 Values", x = "Artist", y = "Count") +
  theme_minimal()

>>>>

@@

![](images/lr_ds_orig.jpeg)

@@

selected_data <- read_csv(here::here("inputs/data/selected_data.csv"))

@@

I Think He Knows by Taylor Swift, plainly, seems danceable to me.

However, personally, I don't hear Taylor Swift's Vigilante Shit or Florence and the Machine's Heaven is Here as danceable. They aren't understated, ambient tracks either -- there's something coercing your body to do something. Like Gamman's description of Antonoff's vocal design sounding how they sound to person who's singing them, the tracks seem like they're trying to get inside of your skin. But they don't have the rhythm of a dance track.

In a lot of ways, I Wanna Get Better by Bleachers is very similar to the typical Antonoff track that the outputs of our RF describe. This song is more anthemic, closer to the driving-over-the-Brooklyn-bridge, sort of post-Springsteen emotions that Antonoff is often characterized (or admitting) to striving for, than danceable. It also seems like it's trying to coercing your attention, if not your body, and the speechiness, loudness, and energy which are so correlated with danceability in Antonoff's RF results are all apparent. The redemption, broken-but-getting-better-quasi-valence can also be heard in the lyrics, but it still doesn't have the kind of rhythm for dancing.

Cornelia Street by Taylor Swift is another sort of almost-danceable track -- while the melody is catchy, the lyrics themselves are wistful. The vocal treatment, again, is there --

@@
